EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-08-13 draft.tex
Section header removed
Update general setup

\subsubsection{Setup} % Even if it's a sub-sub section, flesh this out ... - JJ
\label{setup:local-cloud}

@@

We have deployed the EvoSwarm application locally in the same hardware and
software described in Section~\ref{setup:local-cloud}, additionally the BBOB
experiments were performed with COCO \cite{hansen2016coco} version bbob.v15.03
in Python, the plots were produced with version 2.3.2.

>>>>

%\subsubsection{Setup} % Even if it's a sub-sub section, flesh this out ... - JJ
%\label{setup:local-cloud}

@@

We have deployed the EvoSwarm application in Amazon Elastic Container Service as described in Section~\ref{cloud-aws}, 
additionally the BBOB experiments were performed with COCO \cite{hansen2016coco} version bbob.v15.03
in Python, the plots were produced with version 2.3.2.
